% "Dhruv" CV Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, 10pt]{article}
\usepackage{microtype}
\usepackage{fontspec}
\setmainfont{Arial}

\usepackage[english]{babel}

\usepackage{geometry}
\geometry{left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm}
% Prevent words from breaking like hell-o
\usepackage[none]{hyphenat}

% Give LaTeX flexibility to avoid overflow
\tolerance=1000
\emergencystretch=10em

\usepackage{xcolor}
\definecolor{headerblue}{RGB}{64, 90, 170}

\usepackage{hyperref}
\usepackage[normalem]{ulem}

\hypersetup{
    colorlinks=true,
    linkcolor=headerblue,
    urlcolor=headerblue,
    citecolor=headerblue,
    pdftitle={Dhruv - CV},
    pdfauthor={Dhruv}
}

\newcommand{\cvlink}[2]{\href{#1}{\textcolor{headerblue}{\uline{#2}}}}

\usepackage{enumitem}
\setlist[itemize]{
    nosep,
    topsep=0pt,
    partopsep=0pt,
    leftmargin=1.2em,
    labelsep=0.4em
}

\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\color{headerblue}\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\usepackage{tabularx}

\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS
%----------------------------------------------------------------------------------------

\newcommand{\entry}[4]{
    \noindent\begin{tabularx}{\linewidth}{@{} X r @{}}
        \textbf{\color{headerblue}#1} & \textit{#2} \\
        \textit{#3} & \textit{#4} \\
    \end{tabularx}
}

\newcommand{\expentry}[4]{
    \noindent\begin{tabularx}{\linewidth}{@{} X r @{}}
        \textbf{\color{headerblue}#1} & \textit{#2} \\
        \textit{#3} & \textit{#4} \\
    \end{tabularx}
    \par\vspace{-10pt}
}

\newcommand{\projectentry}[2]{
    \noindent\begin{tabularx}{\linewidth}{@{} X r @{}}
        \textbf{\color{headerblue}#1} & \textit{#2} \\
    \end{tabularx}
    \par\vspace{2pt}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------

\noindent
\begin{tabularx}{\linewidth}{@{} X r @{}}
{\huge \textbf{\color{headerblue} Dhruv}} & \\[4pt]
LinkedIn: \cvlink{https://www.linkedin.com/in/dhruv-ds}{www.linkedin.com/in/dhruv-ds}
& Email: \cvlink{mailto:dhr1249.lm@gmail.com}{dhr1249.lm@gmail.com} \\
GitHub: \hspace{0.22cm}\cvlink{https://github.com/Dhruv1249}{github.com/Dhruv1249}
& Mobile: +91 7876503573 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section*{SKILLS}
\noindent\begin{tabularx}{\linewidth}{@{} l X @{}}
    \textbf{\color{headerblue}Languages:} & Python, JavaScript, TypeScript, Rust, x86 Assembly \\
    \textbf{\color{headerblue}Frontend:} & HTML/CSS, React, Tailwind CSS, Next.js \\
    \textbf{\color{headerblue}Backend:} & Node.js, Express.js, FastAPI, Firebase, MongoDB \\
    \textbf{\color{headerblue}Cloud/DevOps:} & GCP, AWS, Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD, Prometheus, Grafana \\
    
    \textbf{\color{headerblue}Soft Skills:} & Problem-Solving, Time Management, Teamwork, Adaptability \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{EXPERIENCE}

\expentry{Freelance Full Stack Developer $|$ \cvlink{https://varanasitoursindia.com/}{Project Link}}{Nov '25 – Present}{}{}

\begin{itemize}
\item Developed a \textbf{responsive, mobile-first client website} utilizing modern web technologies, optimizing UI/UX design and significantly improving page load speeds for better SEO rankings.
\item Automated \textbf{100\% of billing workflows} by dynamically generating downloadable PDF invoices directly from user orders, eliminating manual invoice creation and streamlining the checkout experience.
\item Architected an automated \textbf{NodeMailer-based email system} integrated with dynamic templating to instantly process customer enquiries, drastically reducing average response times.
\item Integrated \textbf{Firebase} as a centralized database to securely capture, store, and manage incoming lead and enquiry data, improving customer relationship tracking.
\item Synchronized dynamic product catalogs programmatically via the \textbf{Google Sheets API}, enabling non-technical staff to seamlessly update website listings without requiring backend redeployments.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\section*{PROJECTS}
\begingroup
\sloppy
\projectentry{PR Tracker – Agentic AI-Powered Pull Request Management $|$ \cvlink{https://github.com/Dhruv1249/Pr-Tracker}{GitHub Link} $|$ \cvlink{https://pr-tracker.dev}{Live Link}}{Feb '26 - May '26}
\begin{itemize}
\item Built a \textbf{6-service MERN app} with an \textbf{Agentic AI layer} (Gemini API) for autonomous PR summarization and insights.
\item Implemented secure, stateless authentication using \textbf{GitHub OAuth} and \textbf{JWT-based sessions} across distributed microservices, eliminating server-side session storage overhead.
\item Deployed a \textbf{multi-cloud failover environment} (GCP, AWS, Oracle K3s) to ensure high availability globally reliably.
\item Monitored cluster health and resource usage in real-time using \textbf{Prometheus} and \textbf{Grafana dashboards}, enabling early detection of performance bottlenecks.
\item Automated zero-downtime CI/CD deployment pipelines utilizing \textbf{GitHub Actions} and \textbf{Jenkins workflows}, reducing manual deployment effort across all microservices.
\item[] \textbf{Tech:} MERN, Docker, K3s, GCP, AWS, Oracle Cloud, Prometheus, Grafana, Jenkins, GH Actions
\end{itemize}

\vspace{0.5em}

\projectentry{CALYX – ML-Based Global Phenology Forecasting $|$ \cvlink{https://github.com/Dhruv1249/Plant-Phenology-State-Detector}{GitHub Link} $|$ \cvlink{https://plant-phenology-state-detector.vercel.app/}{Live Link}}{Sep '25 - Oct '25}
\begin{itemize}
\item Orchestrated a \textbf{backend data pipeline} processing a \textbf{24GB climate dataset} from NASA and iNaturalist efficiently.
\item Designed a \textbf{low-latency global map interface} enabling region-based ecological forecasting worldwide, \hspace{0.5em} reliably.
\item Trained \textbf{temporal-data regression models} achieving \textbf{75\% prediction accuracy} for plant stages across diverse global climate zones.
\item Integrated the \textbf{Gemini API} to \hspace{0.33em}  generate natural language \hspace{0.33em}  summaries describing detected plant and pest \hspace{0.33em} species.
\item Containerized the full-stack web application with \textbf{Docker} and deployed via \textbf{Google Cloud Run}, ensuring consistent performance under variable traffic loads.
\item[]\textbf{Tech:} Next.js, TypeScript, Python, FastAPI, Gemini API, Docker, Google Cloud Run (GCP)
\end{itemize}
\endgroup


%-----------------------------------------------------
% Open Source
%-----------------------------------------------------

% \section*{OPEN SOURCE}

% \projectentry{Arch Linux Installer (archinstall) \textbar{} \cvlink{https://github.com/archlinux/archinstall/pull/4446}{Merged PR \#4446}}{Apr '26}

% \begin{itemize}
% \item Completed and validated \textbf{Hindi (hi) locale}, fixing fuzzy entries and ensuring full translation coverage
% \item Corrected locale metadata and verified changes using \textbf{locale\_generator} and \textbf{pytest}
% \end{itemize}


%-----------------------------------------------------
% Achievement
%-----------------------------------------------------

\section*{Achievement}

\projectentry{\textbf{NASA Space Apps Challenge 2025} $|$ Global Honorable Mention $|$ \cvlink{https://drive.google.com/file/d/1RZ63Tk5zmSds2Rza-F8y-gWo6T2NvS6H/view?usp=sharing}{Link}}{Nov '25}

\begin{itemize}


\item Recognized among the \textbf{Top 23 global teams} out of \textbf{11,500+ submissions}

\end{itemize}

% ----------------------------------------------------------------------------------------
% 	CERTIFICATES
% ----------------------------------------------------------------------------------------

% \section*{CERTIFICATION}

% \begin{itemize}

% \item Oracle Cloud Infrastructure 2025 AI Foundations Associate $|$ Oracle University $|$ \cvlink{https://drive.google.com/file/d/1lEJNc8hZzfi4_6DZr4nOwpJpimiurhfn/view?usp=sharing}{Link} \hfill\textit{May '26}

% \end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{EDUCATION}

\entry{Lovely Professional University}{Phagwara, Punjab}{Bachelor of Technology - Computer Science and Engineering; \textbf{CGPA: 8.66}}{Since Apr '23}

\entry{G.A.V Sr. Sec. School}{Kangra, Himachal Pradesh}{Intermediate; \textbf{Percentage: 83}}{Apr '22 – Mar '23}

\entry{M.V.M Public High School}{Kangra, Himachal Pradesh}{Matriculation; \textbf{Percentage: 96}}{Apr '20 – Mar '21}

\end{document}