\documentclass[letterpaper, 11pt]{article}

% ─── Packages ────────────────────────────────────────────────────────────────
\usepackage{fontspec}
\usepackage[letterpaper, margin=0.3in, top=0.2in, bottom=0.2in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[none]{hyphenat}
\usepackage{fontawesome5}

% ─── Font ────────────────────────────────────────────────────────────────────
\setmainfont{Carlito}

% ─── Hyperref ────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

% ─── Section Formatting ──────────────────────────────────────────────────────
\titleformat{\section}
  {\normalsize\bfseries}
  {}
  {0em}
  {}
  [\vspace{-6pt}\rule{\linewidth}{0.6pt}\vspace{-2pt}]

\titlespacing{\section}{0pt}{6pt}{4pt}

% ─── List Formatting ─────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=2.2em,
  label=\textbullet,
  itemsep=0pt,
  parsep=0pt,
  topsep=2pt,
  partopsep=0pt
}

% ─── No paragraph indent / tight paragraph spacing ───────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ─── Helper: entry row (bold title | italic tech | right-aligned date) ───────
\newcommand{\cventry}[3]{%
  \noindent
  \textbf{#1}%
  \ifx&#2&\else\enspace\textit{| #2}\fi%
  \hfill\textbf{#3}\par
  \vspace{1pt}%
}

% ─── Helper: certificate/training row ────────────────────────────────────────
\newcommand{\certentry}[3]{%
  \noindent\textbf{#1}\hfill #2\par
  \noindent\textit{#3}\par
  \vspace{3pt}%
}

% ─── Helper: education row ───────────────────────────────────────────────────
\newcommand{\eduentry}[4]{%
  \noindent\textbf{#1}\hfill\textbf{#2}\par
  \noindent\textit{#3}\hfill\textit{#4}\par
  \vspace{3pt}%
}

% ─────────────────────────────────────────────────────────────────────────────


\begin{document}
\pagestyle{empty}

\begin{center}
  {\Huge\bfseries Dhruv}\par
  \vspace{2pt}
  Kangra, Himachal Pradesh 176001\par
  \vspace{2pt}
  {\small
\faPhone\enspace +91\,7876503573 \quad
\faEnvelope\enspace \href{mailto:dhruv1249.lm@gmail.com}{dhruv1249.lm@gmail.com} \quad
\faLinkedin\enspace \href{https://www.linkedin.com/in/dhruv-ds}{linkedin.com/in/dhruv-ds} \quad
\faGithub\enspace \href{https://github.com/Dhruv1249}{github.com/Dhruv1249}
}
\end{center}

\vspace{2pt}

\section{Experience}

\cventry{Freelance Full Stack Developer $|$ \href{https://varanasitoursindia.com/}{Project Link}}{}{Nov '25 -- Feb '26}
\begin{itemize}
 \item Developed responsive, \textbf{mobile-first} websites, optimizing \textbf{UI/UX} design and page load performance for better \textbf{SEO} rankings.
\item Automated billing workflows by dynamically generating downloadable \textbf{PDF invoices} directly from user orders, removing manual invoicing entirely.
\item Architected automated \textbf{NodeMailer} email workflows with \textbf{dynamic templating} for the instant live customer enquiry handling.
\item Integrated \textbf{Firebase} to securely capture and manage incoming leads, and utilized the \textbf{Google Sheets API} to synchronize product catalogs.
\end{itemize}


\section{Projects}

\vspace{3pt}
\cventry{PR Tracker -- Agentic AI-Powered PR Management}{MERN, K3s, GCP, AWS, Prometheus, Grafana}{Feb '26 -- May '26}
\begin{itemize}
  \item Designed a \textbf{6-service MERN architecture} featuring an \textbf{Agentic AI layer} (powered by \textbf{Gemini API}) for autonomous pull request summarization and risk analysis.
  \item Engineered a secure authentication gateway utilizing \textbf{GitHub OAuth} alongside \textbf{JWT-based session management} with strict role-based access control.
  \item Built a \textbf{multi-cloud failover} via GCP to Oracle K3s and AWS, ensuring high availability along with \textbf{Prometheus} and \textbf{Grafana}.
  \item Automated CI/CD pipelines utilizing \textbf{GitHub Actions} and \textbf{Jenkins} to ensure seamless, zero-downtime container rollouts across environments.
  \item [] Repository Link : \href{https://github.com/Dhruv1249/Pr-Tracker}{\textbf{GitHub}} \quad
        Live Link : \href{https://pr-tracker.dev}{\textbf{Live}}
\end{itemize}

\vspace{3pt}
\cventry{CALYX -- ML-Based Global Phenology Forecasting}{Next.js, Python, FastAPI, Docker, GCP}{Sep '25 -- Oct '25}
\begin{itemize}
 \item Orchestrated \textbf{backend architecture} and \textbf{climate data pipeline} processing 24GB from \textbf{NASA MERRA-2}, \textbf{ERA5}, \textbf{iNaturalist}, and \textbf{K{\"o}ppen}, powering a global map interface for region-based ecological forecasting.
  \item Trained temporal-data regression models on historical climate records, achieving \textbf{75\% prediction accuracy} across plant species.
\item Containerized and deployed the \textbf{full-stack application} via \textbf{Docker} on \textbf{Google Cloud Run} for scalable, on-demand infrastructure.
  \item [] Repository Link : \href{https://github.com/Dhruv1249/Plant-Phenology-State-Detector}{\textbf{GitHub}} \quad
        Live Link : \href{https://plant-phenology-state-detector.vercel.app/}{\textbf{Live}}
\end{itemize}



\section{Achievement}

\cventry{NASA Space Apps Challenge $|$ Global Honorable Mention $|$ \href{https://drive.google.com/file/d/1RZ63Tk5zmSds2Rza-F8y-gWo6T2NvS6H/view?usp=sharing}{Link}}{}{Nov '25}
\begin{itemize}
  \item Recognized among the Top 23 global teams out of 11,500+ submissions.
\end{itemize}

\vspace{3pt}
% \cventry{Achievers Award $|$ Lovely Professional University $|$ \href{https://drive.google.com/file/d/1jUvyxd_S2_XL_4Awme9gFDLHbbeuwkiq/view?usp=sharing}{Link}}{}{Nov '25}
% \begin{itemize}
%   \item Awarded for outstanding performance in competitive hackathons.
% \end{itemize}

\section{Certification}

\certentry{Oracle Cloud Infrastructure 2025 AI Foundations Associate}{\textbf{May '26}}{Oracle University --- \href{https://drive.google.com/file/d/1lEJNc8hZzfi4_6DZr4nOwpJpimiurhfn/view?usp=sharing}{Certificate Link}}
% \certentry{Introduction to Large Language Models}{\textbf{Apr '25}}{NPTEL --- \href{https://drive.google.com/file/d/1Ypk5IU8V_YzrDsZ1wsVm00OnfqWnwZol/view?usp=sharing}{Certificate Link}}

\section{Skills}


\hangindent=7em
\noindent\makebox[7em][l]{\textbf{Languages:}} Python, JavaScript, TypeScript, Rust, x86 Assembly\par
\vspace{2pt}
\hangindent=7.22em
\noindent\makebox[7em][l]{\textbf{Technologies:}} React, Node.js, Express.js, FastAPI, MongoDB, Docker, Docker Compose, Google Cloud Platform, AWS, Oracle Cloud, Kubernetes, Prometheus, Grafana\par
\vspace{2pt}
\hangindent=7em
\noindent\makebox[7em][l]{\textbf{Domain Skills:}} Machine Learning, Data Processing, Backend Development, Systems Programming, Problem-Solving


\section{Education}

\eduentry{Lovely Professional University}{Aug '23 -- Present}
  {Bachelor of Technology -- Computer Science and Engineering \quad CGPA: 8.66}{Phagwara, Punjab}

\eduentry{G.A.V Sr. Sec. School}{Apr '22 -- Mar '23}
  {Intermediate --- Percentage: 83}{Kangra, Himachal Pradesh}

\eduentry{M.V.M Public High School}{Apr '20 -- Mar '21}
  {Matriculation --- Percentage: 96}{Kangra, Himachal Pradesh}

\end{document}